Supplementary material

### 2019-06-13 paper/related.tex
new reference

\subsection{Cluster characterisation}
While visualisation has gained prominence as a crucial component of scientific
discovery, justification, and communication \todo{Add Cites: maybe Gelman?
Tufte?}, visually representing evolving spatial data is a challenging old
problem~\citep{monmonier1990strategies,andrienko2003exploratory,ferreira2015visual,Zheng2016}.

>>>>

\subsection{Cluster characterisation}
While visualisation has gained prominence as a crucial component of scientific
discovery, justification, and communication~\cite{tufte1998visual}, visually
representing evolving spatial data is a challenging old
problem~\citep{monmonier1990strategies,andrienko2003exploratory,ferreira2015visual,Zheng2016}.

### 2019-06-13 sup/sup.tex
new reference

\begin{document}

@@

\section{Original request for feedback}
As part of our efforts in the Urban Genome Project of the University of Toronto,
we are trying to build infrastructure to help understand recurrent and
distinctive patterns of urban change.

@@

This prototype is part of an article, to be submitted to the next IEEE VIS
conference, and we are humbly requesting feedback on how effective it actually
is.

@@

\href{http://ug.daniels.utoronto.ca/~diasf/CTEvo/doc.html}{\url{http://ug.daniels.utoronto.ca/~diasf/CTEvo/doc.html}}

@@

\href{https://www.youtube.com/watch?v=OZFUA0ThEaY&list=PLBd6KRI4PG-RcxAX35OfHd1DKl3qWfXRV}{youtube}

@@

\href{http://ug.daniels.utoronto.ca/~diasf/CTEvo/}{\url{http://ug.daniels.utoronto.ca/~diasf/CTEvo/}}

@@

\section{Expert comments}
\subsection{A - Cary Wu}
%\href{https://soci.ubc.ca/persons/cary-wu/}{\url{https://soci.ubc.ca/persons/cary-wu/}}
\emph{Doctoral candidate in Sociology at the University of British Columbia, Canada.}

@@

\subsection{B - Ethan Fosse}
% \href{https://scholar.harvard.edu/ethanfosse}{\url{https://scholar.harvard.edu/ethanfosse}}
\emph{Research Associate at Princeton University, USA}

@@

\subsection{C - Fernando Calderón Figueroa}
\emph{Doctoral candidate in Sociology at the University of Toronto, Canada}

@@

\subsection{D - Patrick Adler}
\emph{Research Associate at the Martin Prosperity Institute, Canada.}

@@

\subsection{E - James Murdoch}
\emph{Policy Analyst at 2M Research, USA}

>>>>

\newcommand{\censure}[1]{}
\begin{document}

@@

\section{Original request for feedback}
As part of our efforts in \censure{the Urban Genome} Project of the
\censure{University of Toronto}, we are trying to build infrastructure to help
understand recurrent and distinctive patterns of urban change.

@@

This prototype is part of an article, and we are humbly requesting feedback on
how effective it actually is.

@@

\censure{\href{http://ug.daniels.utoronto.ca/~diasf/CTEvo/doc.html}{\url{http://ug.daniels.utoronto.ca/~diasf/CTEvo/doc.html}}}

@@

\censure{\href{https://www.youtube.com/watch?v=OZFUA0ThEaY&list=PLBd6KRI4PG-RcxAX35OfHd1DKl3qWfXRV}{youtube}}

@@

\censure{\href{http://ug.daniels.utoronto.ca/~diasf/CTEvo/}{\url{http://ug.daniels.utoronto.ca/~diasf/CTEvo/}}}

@@

\section{Expert comments}

\subsection{A\censure{ - Cary Wu}}
\censure{\emph{Doctoral candidate in Sociology at the University of British Columbia, Canada.}}

@@

\subsection{B\censure{ - Ethan Fosse}}
% \href{https://scholar.harvard.edu/ethanfosse}{\url{https://scholar.harvard.edu/ethanfosse}}
\censure{\emph{Research Associate at Princeton University, USA}}

@@

\subsection{C \censure{- Fernando Calderón Figueroa}}
\censure{\emph{Doctoral candidate in Sociology at the University of Toronto, Canada}}

@@

\subsection{D\censure{ - Patrick Adler}}
\censure{\emph{Research Associate at the Martin Prosperity Institute, Canada.}}

@@

\subsection{E\censure{ - James Murdoch}}
\censure{\emph{Policy Analyst at 2M Research, USA}}
